Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 cross_compilation.tex

\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation}

@@

@@

env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
env.user = 'root'
env.password = 'sdn'

@@

\subsection{Long running jobs over SSH (PUT THIS SECTION SOMEWHERE ELSE)}

Problem when you logout, then applications will terminate. SCREEN is the answer.

EXAMPLE

\texttt{hello\_world} returns immediately. This is not always the case.
Sometimes it is desired to run simulations that should run for days. 
A software package called \texttt{screen} can be used for this purpose.
Simply run ...

>>>>

\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation (WHAT IS THE PURPOSE OF THIS SUBSECTION?)}

@@

Often when simplicity and fast prototyping is of higher importance than speed
it is often desired to use a scripting language rather than the often faster
compiled language. Kodo-python provides roughly similar bindings to the
underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
python calls to Kodo-python are actually executed in the underlying C++11
compilied code.

Parsing calls and variables between Python and C++ compiled code is
not free, but this small introduced overhead may in many cases be worth
it to take advantage of Pythons and other scripting languages many
benefits.

Below is a short procedure to use Kodo-python in a \ac{Raspi}.

One advantage of Python compared to Kodo-cpp is that only the Kodo-python
library needs to be cross compiled. The python scripts using the Kodo
library needs not to be cross compiled but simply copied to the same
directory as .

Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.

\begin{lstlisting}[]
$ apt-get update
$ apt-get install python build-essential libpython-dev python-dev
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
% IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED

Create a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\begin{lstlisting}[]
$ git clone git@github.com:steinwurf/kodo-python.git 
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\begin{lstlisting}[]
$ cd kodo-python
$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
$ python waf build
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.

@@

env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
env.user = 'pi'
env.password = 'raspberry'

@@

\subsection{Long running jobs using SSH}

There may be times when it is desired to start a simulation that will
run for days. For that purpose, it may not be desired to keep
a \ac{SSH} connection open to the \ac{Raspi} risking that the connection
will be interrupted and thus result in the \ac{Raspi} terminating
the running simulation.

There exists a few methods to avoid this risk of simulations terminating
unexpectedly. One method is to run a program within a \texttt{screen} session.

\texttt{screen} enables a user to attach and detach the session as it is
desired. Programs within the screen session just keeps running.

The following procedure will present how to use SSH to
\begin{enumerate}
    \item login to a \ac{Raspi}
    \item open a screen session
    \item execute a command
    \item detach from the screen session
    \item terminate SSH connection
    \item login to the \ac{Raspi} again
    \item attach to screen session to see the program still running
\end{enumerate}

Start by establishing SSH connection to a \ac{Raspi} and open a screen session:
\begin{lstlisting}[]
$ SSH pi@<RASP_IP>
$ screen
Screen version 4.02.01 (GNU) 28-Apr-14
...
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
Press space or return to to clear the shell.

At this stage, we are in a screen session. Now execute a program that never ends:
\begin{lstlisting}[]
$ top
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Now that \texttt{top} is running, press Ctrl+a Crtl+d to detach from
the \texttt{screen} session.

Terminate the SSH connection and login again:
\begin{lstlisting}[]
$ exit
$ SSH pi@<RASP_IP>
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Now that we are logged in to the \ac{Raspi} again, lets see if a
\texttt{screen} session is still running:
\begin{lstlisting}[]
$ screen -list
There is a screen on:
	1668.pts-0.rasp09	(06/06/16 04:02:15)	(Detached)
1 Socket in /var/run/screen/S-pi.
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

It can be seen that our session is still running and that we are
currently not attached. Lets attach to the session:
\begin{lstlisting}[]
$ screen -r 1668.pts-0.rasp09
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

After attaching again, \texttt{top} should still be running. \texttt{screen}
has a few more useful functionalities that is outside the scope of this
paper.

To terminate the \texttt{screen} session. First, terminate \texttt{top}
by pressing 'q', and then type 'exit' two times to first exit the
\texttt{screen} session and then terminate the \ac{SSH} connection:

%Problem when you logout, then applications will terminate. SCREEN is the answer.

%\texttt{hello\_world} returns immediately. This is not always the case.
%Sometimes it is desired to run simulations that should run for days. 
%A software package called \texttt{screen} can be used for this purpose.
%Simply run ...
